%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\newcommand\tab[1][2.5cm]{\hspace*{#1}}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{1.7in}
\addtolength{\footskip}{-0.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {\small #1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textbf{\textit{\small#3}} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\huge \scshape Rudra Joshi} \\ \vspace{2pt}
    \small AI / ML Engineer (GenAI $\cdot$ RAG $\cdot$ LLMs $\cdot$ FastAPI) \\ \vspace{4pt}
    \small \raisebox{-0.1\height}\faPhone\ +61 466988797 ~
    \href{mailto:rudrajoshi.cs@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ rudrajoshi.cs@gmail.com} ~
    Sydney, New South Wales, Australia ~
    \href{https://www.linkedin.com/in/rudrajoshi25/}{\raisebox{-0.2\height}\faLinkedin\ linkedin.com/in/rudrajoshi25/} ~
    \href{https://github.com/RudraJoshi25}{\raisebox{-0.2\height}\faGithub\ github.com/RudraJoshi25}
    \vspace{-8pt}
\end{center}

\vspace{-16pt}

% %-----------SUMMARY-----------
% \section{Summary}
% \begin{itemize}[leftmargin=0.15in, label={}]
%   \small{\item{
%     AI/ML engineer with hands-on experience building and deploying production RAG pipelines, LLM-powered APIs, and ML anomaly detection systems. Skilled in LangChain, FastAPI, Python, and cloud deployment. Holds an MCS from the University of Wollongong and brings a research background including an IEEE Best Paper Award and a government-filed patent. Seeking AI/ML or GenAI engineering roles where I can contribute to real-world systems from day one.
%   }}
% \end{itemize}

% \vspace{-20pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
     \small{\item{
    \textbf{Programming}{: Python, SQL, JavaScript, TypeScript} \\
    \textbf{Data \& Analytics}{: Pandas, NumPy, SQL window functions, cohort/funnel analysis, segmentation, retention analytics} \\
    \textbf{ML Modeling}{: scikit-learn, supervised learning, PyTorch, TensorFlow, classification/regression, feature engineering, cross-validation, hyperparameter tuning, class imbalance handling} \\
    \textbf{Evaluation}{: ROC-AUC, PR-AUC, precision/recall/F1, calibration, interpretability (SHAP/feature importance)} \\
   \textbf{Cloud \& Platforms}{: Azure (AI Services, API Management \textit{-- actively upskilling}), AWS (S3, API Gateway, Lambda), GCP (BigQuery), Redshift, Databricks, Snowflake} \\
   \textbf{GenAI}{: LLMs (OpenAI API, Azure OpenAI, Anthropic Claude, Groq), prompt engineering, RAG, embeddings, vector search, grounding/hallucination mitigation, LangChain/LlamaIndex} \\
    \textbf{MLOps}{: Docker, CI/CD, Git, model deployment/monitoring}
  }}
\end{itemize}

\vspace{-20pt}


%-----------PROJECTS-----------------
\section{Key Projects}
\vspace{-1pt}
\begin{itemize}[leftmargin=0.0in, label={}]

\item \small \textbf{PersonaQuery} \href{https://personaquery.vercel.app/}{\small [Live]} \hfill \small \textbf{Customer-style PoC - Production-ready AI Application}
\vspace{-9pt}
\begin{itemize}[leftmargin=0.4cm]
% \item \small Built an end-to-end \textbf{anomaly detection pipeline} across \textbf{structured health signal data} (time-series metrics) and \textbf{unstructured log inputs}; threshold tuning reduced false positive alert rate by approx. 40\%, covering preprocessing, feature extraction, scoring, and alert rule execution (Python, FastAPI).
\vspace{-3.5pt}
\item \small Applied \textbf{product-style requirements discovery} (use cases + success metrics) and iterated UX to enable fast stakeholder reviews --- mirroring a PoC validation process.
\item \small Implemented an \textbf{evaluation harness} with a small \textbf{golden set} (expected answers + citations) to regression-test retrieval quality across prompt/retrieval changes.
\vspace{-3.5pt}
\item \small Added {guardrails} (schema validation + citation-required responses) and production hardening ({error handling, logging,} rate-limit aware usage); designed as {modular components} (retrieval, reranking, generation) with clean service boundaries to improve reliability and maintainability.
\vspace{-3.5pt}
\item \small Shipped as a \textbf{PoC-to-production service} with CORS-safe integration and deployment trade-offs (latency/cost) measured via p95 timings.
\vspace{-3.5pt}
\item \small \textbf{Tech:} LangChain/LlamaIndex, Groq (Llama-3.3-70B), Sentence-Transformers (all-MiniLM-L6-v2), Hybrid retrieval (BM25 + vectors), FastAPI/Uvicorn, Render + Vercel.
\vspace{-3.5pt}
\end{itemize}
\vspace{-10pt}

\item \small \textbf{HealthEcho} \href{https://healthecho.vercel.app/}{\small [Live]} \hfill \small \textbf{Production ML System, Monitoring, FastAPI}
\vspace{-9pt}
\begin{itemize}[leftmargin=0.4cm]
\item \small Built an end-to-end {anomaly detection pipeline} handling {inconsistent and incomplete sensor inputs} across structured health signal data (time-series metrics) and unstructured log inputs; threshold tuning reduced false positive alert rate by approx. 40\%, covering preprocessing, feature extraction, scoring, and alert rule execution (Python, FastAPI).
\vspace{-3.5pt}
% \item \small Evaluated detector quality using \textbf{precision/recall} and tuned thresholds to control \textbf{false positives}; added logging to track alert volume and error cases over time.
% \vspace{-3.5pt}
\item \small Deployed \textbf{batch scoring + inference API} with REST endpoints and validation; integrated alerting workflow and structured observability logs for debugging and monitoring.
\vspace{-3.5pt}
\item \small \textbf{Tech:} Next.js (React, TypeScript), Node.js/Express, FastAPI, SQL, deployment on Vercel; env vars + CORS-safe API integration.
\vspace{-3.5pt}
\end{itemize}
\vspace{-10pt}

\item \small \textbf{AI Job Scout} \hfill \small \textbf{Multi-Agent System, MCP, Agentic Scraping}
\vspace{-9pt}
\begin{itemize}[leftmargin=0.4cm]
\item \small Built a \textbf{multi-agent pipeline} using MCP to autonomously scrape, filter, and rank job listings based on relevance to a target profile --- coordinating agents across search, extraction, and scoring stages.
\vspace{-3.5pt}
\item \small Designed agent communication with \textbf{clean task boundaries} (search agent, parser agent, ranking agent) to enable modular iteration and reduce inter-agent coupling.
\vspace{-3.5pt}
\item \small \textbf{Tech:} MCP, multi-agent orchestration, Python, web scraping, FastAPI.
\vspace{-3.5pt}
\end{itemize}
\vspace{-10pt}

\end{itemize}

\vspace{-14pt}

%-----------PUBLICATIONS------------
\section{Publications \& Patents}
\vspace{-2pt}
\begin{itemize}[leftmargin=0.3cm]
\small{
    \item \textbf{Patent} --- Indian Government: \textit{Intelligent Face Recognition System Using Deep Recurrent Neural Network} (Application No. 202211058943 A)
    \vspace{-6pt}

\item R. Joshi, A. Vyas, et al., \textbf{``Cognitive-Chair: AI based advanced Brain Sensing Wheelchair for Paraplegic/Quadriplegic people,''} AIST 2022 \textbf{[Best Paper Award]}, IEEE Xplore 2023 \href{https://ieeexplore.ieee.org/abstract/document/10065338}{[Link to Paper]}
    \vspace{-7pt}
}
\end{itemize}

\vspace{-14pt}
%-----------EXPERIENCE-----------
\section{Work Experience}
\vspace{-1pt}
\resumeSubHeadingListStart

\resumeSubheading
{TSPL}{Jan 2023 -- Jun 2023}
{\textbf{Junior Android Application Development Intern}}{Vadodara, India}
\begin{itemize}[leftmargin=*]
\vspace{-1pt}
\item \small Built an Android app end-to-end with backend REST APIs; integrated charts for analytics views. (Java/Spring Boot, MySQL)
\vspace{-4pt}
\item \small Delivered features across UI $\leftrightarrow$ API $\leftrightarrow$ DB with clean endpoint design and predictable payload contracts.
\vspace{-4pt}
\end{itemize}
\vspace{-6pt}

\resumeSubheading
{Gurukula, Tntra Engineering}{Sep 2022 -- Dec 2022}
{\textbf{Multi Domain Intern}}{Vadodara, India}
\begin{itemize}[leftmargin=*]
\vspace{-1pt}
\item \small Completed multi-domain engineering training + team project delivery under senior developer guidance (web dev / cloud / cyber).
\vspace{-4pt}
\end{itemize}
\vspace{-6pt}

\resumeSubheading
{Gurukula, Tntra Engineering}{Jun 2022 -- Jul 2022}
{\textbf{Full Stack Intern (Summer Intern)}}{Vadodara, India}
\begin{itemize}[leftmargin=*]
\vspace{-1pt}
\item \small Built and shipped small web app modules in an industry workflow (tickets, reviews, iterative delivery).
\vspace{-4pt}
\end{itemize}
\vspace{-5pt}

\resumeSubHeadingListEnd

\vspace{-23pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Wollongong}{Wollongong, Australia}
      {Master of Computer Science}{}
     \vspace{-9pt}
    \begin{itemize}[leftmargin=0.1in, label={}]
        \item {\textbf{Coursework}: Data Mining, Machine Translation, Algorithms for Data Science, Intro to Optimization.}
    \end{itemize}
    \vspace{-9pt}
    \resumeSubheading
      {Gujarat State Fertilizers and Chemicals University}{Vadodara, India}
      {Bachelor of Technology in Computer Science \& Engineering with Specialization in Data Science}{}
    \vspace{-9pt}
    \begin{itemize}[leftmargin=0.1in, label={}]
        \item{\textbf{Coursework}: Data Structures \& Algorithms, Machine Learning for Intelligent Systems, Deep Learning, NLP.}
    \end{itemize}
    \vspace{-1pt}
  \resumeSubHeadingListEnd
\vspace{-20pt}

%-----------PUBLICATIONS------------
% \section{Publications}
% \vspace{-2pt}
% \begin{itemize}[leftmargin=0.3cm]
% \small{
%     \item \textbf{Patent} --- Indian Government: \textit{Intelligent Face Recognition System Using Deep Recurrent Neural Network} (Application No. 202211058943 A)
%     \vspace{-6pt}

%     \item R. Joshi, A. Vyas, et al., \textbf{``Cognitive-Chair: AI based advanced Brain Sensing Wheelchair for Paraplegic/Quadriplegic people,''} ``AIST 2022 \textbf{[Won the Best paper award],''} IEEE Xplore Publication 2023 \href{https://ieeexplore.ieee.org/abstract/document/10065338}{[Link to Paper]}
%     \vspace{-7pt}
% }
% \end{itemize}

\end{document}